### 2018-03-26 Writing/draft.tex
changed number of simulations from 40 to 35

\item \textbf{Inferring topologies}: we inferred the topologies from the ``normal'', ``maximised'', ``minimised'' and ``randomised'' matrices using both maximum parsimony  (MP) and Bayesian inference (BPP). 
Hereafter, the resultant topologies are called the ``normal'', ``maximised'', ``minimised'' and ``randomised'' trees). This step resulted in 72 topologies.
    \item \textbf{Comparing topologies}: finally, we compared the ``normal'' to the ``maximised'', ``minimised'' and ``randomised'' trees to measure the effect of character correlation on topology.
\end{enumerate}
Each step was replicated 40 times and are described below in more detail, along with our proposed definition for measuring the difference between characters.

@@

For each tree with 25, 75 or 150 taxa we generated matrices with 100, 350 and 1000 characters following \cite{OReilly20160081}.
The matrices were generated using the \texttt{dispRity R} package \citep{thomas_guillerme_2016_55646}.
To estimate the variance of our simulations and assess the effect of our random parameters, we repeated this step 40 times resulting in 360 ``normal'' morphological matrices.

\subsection{Modifying the matrices}
We calculated the pairwise character differences for each generated matrix using the \texttt{dispRity R} package \citep{thomas_guillerme_2016_55646}.
We then modified the matrices to either maximise or minimise the pairwise character differences for each matrix using three different algorithms.
For maximising the pairwise differences between characters, we selected the characters that were the most similar to all the others (i.e. with an average character difference $<0.25$) and replaced them randomly by any of the remaining characters.
This operation increased the overall pairwise character difference in the matrix thus making the characters more dissimilar.
Conversely, for minimising the pairwise character differences, we selected the most dissimilar characters (i.e. with an average character difference $<0.75$) and randomly replaced them with the remaining ones.
Finally, because this operation effectively changes the weight of characters (i.e. giving the characters $<0.25$ or $>0.75$ a weight of $0$ and giving the randomly selected remaining characters a weight of +$1$), we randomly replaced the average number of characters replaced in the character maximisation and minimisation by any other characters as a randomised expectation modification (i.e. randomly weighting characters).
% Clever.
Each of the three matrices are effectively a bootstrap pseudo-replication of the ``normal'' matrix with the ``randomised'' one being a random one and the ``maximised'' and ``minimised'' being conditional bootstraps.
This step resulted in a total of 1440 matrices (hereafter called the ``normal'', ``maximised'', ``minimised'' and ``randomised'' matrices - see Fig. \ref{Fig:modif_matrix} for an illustration).
The algorithms for the three modifications are available on GitHub (\url{https://github.com/TGuillerme/CharactersCorrelation})

>>>>

\item \textbf{Inferring topologies}: we inferred the topologies from the ``normal'', ``maximised'', ``minimised'' and ``randomised'' matrices using both maximum parsimony  (MP) and Bayesian inference (BPP). 
Hereafter, the resultant topologies are called the ``normal'', ``maximised'', ``minimised'' and ``randomised'' trees). This step resulted in 72 topologies.
    \item \textbf{Comparing topologies}: finally, we compared the ``normal'' to the ``maximised'', ``minimised'' and ``randomised'' trees to measure the effect of character correlation on topology.
\end{enumerate}
Each step was replicated 35 times and are described below in more detail, along with our proposed definition for measuring the difference between characters.

@@

For each tree with 25, 75 or 150 taxa we generated matrices with 100, 350 and 1000 characters following \cite{OReilly20160081}.
The matrices were generated using the \texttt{dispRity R} package \citep{thomas_guillerme_2016_55646}.
To estimate the variance of our simulations and assess the effect of our random parameters, we repeated this step 35 times resulting in 315 ``normal'' morphological matrices.

\subsection{Modifying the matrices}
We calculated the pairwise character differences for each generated matrix using the \texttt{dispRity R} package \citep{thomas_guillerme_2016_55646}.
We then modified the matrices to either maximise or minimise the pairwise character differences for each matrix using three different algorithms.
For maximising the pairwise differences between characters, we selected the characters that were the most similar to all the others (i.e. with an average character difference $<0.25$) and replaced them randomly by any of the remaining characters.
This operation increased the overall pairwise character difference in the matrix thus making the characters more dissimilar.
Conversely, for minimising the pairwise character differences, we selected the most dissimilar characters (i.e. with an average character difference $<0.75$) and randomly replaced them with the remaining ones.
Finally, because this operation effectively changes the weight of characters (i.e. giving the characters $<0.25$ or $>0.75$ a weight of $0$ and giving the randomly selected remaining characters a weight of +$1$), we randomly replaced the average number of characters replaced in the character maximisation and minimisation by any other characters as a randomised expectation modification (i.e. randomly weighting characters).
% Clever.
Each of the three matrices are effectively a bootstrap pseudo-replication of the ``normal'' matrix with the ``randomised'' one being a random one and the ``maximised'' and ``minimised'' being conditional bootstraps.
This step resulted in a total of 1260 matrices (hereafter called the ``normal'', ``maximised'', ``minimised'' and ``randomised'' matrices - see Fig. \ref{Fig:modif_matrix} for an illustration).
The algorithms for the three modifications are available on GitHub (\url{https://github.com/TGuillerme/CharactersCorrelation})
